\bibliographystyle{plain}
{\raggedright
\begin{thebibliography}{10}
\medskip

\bibitem{\en{EN}agar}
Ravi P. Agarwal, Hans Agarwal \& Syamal K. Sen 
\newblock {Birth, growth and computation of pi to ten trillion digits}.
\newblock {\em Adv Differ Equ} 2013, 100 (2013).
\newblock {\scriptsize\url{https://doi.org/10.1186/1687-1847-2013-100}}.
\medskip

\bibitem{\en{EN}lit02}
Natália Archinard.
\newblock {\em Abelian varieties and identities for hypergeometric series}.
\newblock ETH Zürich, 2000.
\newblock {\scriptsize\url{https://doi.org/10.3929/ethz-a-004070858}}.
\medskip

\bibitem{\en{EN}Borwein:1987:agm}
Jonathan~M.~Borwein and Peter~B.~Borwein.
\newblock {\em Pi and the AGM: A Study in the Analytic Number Theory and
  Computational Complexity}.
\newblock Wiley-Interscience, New York, 1987.
\medskip

\bibitem{\en{EN}Borwein1988}
Jonathan~M.~Borwein and Peter~B.~Borwein.
\newblock More ramanujan-type series for 1/pi.
\newblock {\em Ramanujan revisited: proceedings of the centenary conference},
  1988.
%\newblock  {\scriptsize\url{http://www.cecm.sfu.ca/personal/pborwein/PAPERS/CP4.pdf}}.
\medskip

\bibitem{\en{EN}Buell1989}
Duncan A.~Buell.
\newblock {\em Binary Quadratic Forms}.
\newblock Springer, New York, 1989
\medskip

\bibitem{\en{EN}CohenStromberg}
Henri Cohen and Fredrik Strömberg.
\newblock {\em Modular Forms: A Classical Approach (Graduate Studies in Mathematics)}.
\newblock American Mathematical Society, 2017.
\newblock {\scriptsize\url{https://bookstore.ams.org/gsm-179}}.
\medskip

\bibitem{\en{EN}glebov}
Imin Chen and Gleb Glebov.
\newblock On chudnovsky--ramanujan type formulae.
\newblock {\em The Ramanujan Journal}, Oct 2017.
\newblock {\scriptsize\url{https://doi.org/10.1007/s11139-017-9948-8}}.
\medskip

\bibitem{\en{EN}chud1988}
David~V.~Chudnovsky and Gregory~V.~Chudnovsky.
\newblock Approximation and Complex Multiplication according to Ramanujan.
\newblock {\em Ramanujan Revisited: Proceedings of the Centenary Conference (held at the University of Illinois at Urbana-Champaign, June 1-5, 1987)},
  1988.
\medskip

\bibitem{\en{EN}clausen}
Thomas Clausen.
\newblock Ueber die {F}älle, wenn die {R}eihe von der {F}orm y = 1 + ... etc.
  ein {Q}uadrat von der {F}orm z = 1 ... etc.~hat.
\newblock {\em Journal für die reine und angewandte Mathematik}, 3(3):89--91,
  1828.
\newblock
  {\scriptsize\url{http://www.digizeitschriften.de/dms/img/?PID=PPN243919689_0003&physid=phys94}}.
\medskip

\bibitem{\en{EN}Freitag2000}
Eberhard Freitag \en{and}\de{und} Rolf Busam.
\newblock {\em \en{Complex Analysis}\de{Funktionentheorie 1}}.
\newblock Springer, Berlin, Heidelberg, \en{2009}\de{2006}.
\newblock {\scriptsize\url{\en{https://doi.org/10.1007/978-3-540-93983-2}\de{https://doi.org/10.1007/978-3-662-07352-0}}}.
\medskip

\bibitem{\en{EN}Fricke2}
Robert Fricke.
\newblock {\em Die elliptischen Funktionen und ihre Anwendungen -- Zweiter Teil: Die algebraischen Ausführungen}.
\newblock Teubner, Leipzig, 1922.
\newblock {\scriptsize\url{https://doi.org/10.1007/978-3-642-19561-7}}.
\medskip

\bibitem{\en{EN}archimedes}
Thomas~Little Heath.
\newblock {\em The Works of Archimedes}.
\newblock Cambridge University Press, London, 1897.
\newblock
  {\scriptsize\url{http://www.archive.org/details/worksofarchimede029517mbp/}}.
\medskip

\bibitem{\en{EN}kasten}
Hendrik Kasten.
\newblock {\em Die Ramanujankonstante}.
\newblock Uni Heidelberg, 2013.
\newblock
  {\scriptsize\url{https://www.mathi.uni-heidelberg.de/~kasten/files/Skripte/ss10ramanujan.pdf}}.
\medskip

\bibitem{\en{EN}klein}
Felix Klein und Robert Fricke.
\newblock {\em Vorlesungen über die Theorie der elliptischen Modulfunctionen,
  Bd.1: Grundlegung der Theorie}.
\newblock Teubner, Leipzig, 1890.
\newblock
  {\scriptsize\url{https://archive.org/details/vorlesungenberd05kleigoog}}.
\medskip

\bibitem{\en{EN}Lang1987}
Serge Lang.
\newblock {\em Elliptic Functions}.
\newblock Springer, New York, 1987.
\medskip

\bibitem{\en{EN}Masser1975}
David~W.~Masser.
\newblock {\em Elliptic Functions and Transcendence}.
\newblock Springer, Berlin, Heidelberg, 1975.
\medskip

\bibitem{\en{EN}Milla2021}
Lorenz Milla.
\newblock An efficient determination of the coefficients in the Chudnovskys' series for $1/\pi$.
\newblock {\em Ramanujan Journal}, 2021.
\newblock  {\scriptsize\url{https://doi.org/10.1007/s11139-020-00330-6}}.\\
\newblock %ShortDOI: {\scriptsize\url{https://doi.org/ft53}}. 
\en{Free view-only full-text article:}\de{Frei zugängliche Leseversion:} {\scriptsize\url{https://rdcu.be/ce8Bt}}.
\medskip

\bibitem{\en{EN}rama1914}
Srinivasa Ramanujan.
\newblock Modular equations and approximations to $ \pi $.
\newblock {\em Quarterly Journal of Mathematics}, 45:180, 350--372, 1914.
\newblock
  {\scriptsize\url{http://ramanujan.sirinudi.org/Volumes/published/ram06.pdf}}.
\medskip

\bibitem{\en{EN}Robbins}
Herbert Robbins.
\newblock A Remark on Stirling's Formula.
\newblock {\em The American Mathematical Monthly}, 62(1), 26-29, 1955.
\newblock
  {\scriptsize\url{http://doi.org/10.2307/2308012}}.
\medskip

\bibitem{\en{EN}silverman1994advanced}
Joseph Silverman.
\newblock {\em Advanced topics in the arithmetic of elliptic curves}.
\newblock Springer, New York, 1994.
\medskip

\bibitem{\en{EN}snellius}
Willebrord Snell.
\newblock {\em Cyclometricus}.
\newblock Elsevier, 1621.
\newblock {\scriptsize\url{https://books.google.de/books?id=kZg_AAAAcAAJ}}.
\medskip


\bibitem{\en{EN}WeilElliptic}
Andre Weil.
\newblock {\em Elliptic functions according to Eisenstein and Kronecker}.
\newblock Springer, Berlin, New York, 1976.
\medskip

\bibitem{\en{EN}ycru}
Alexander Yee.
\newblock {\em y-cruncher - A Multi-Threaded Pi-Program}.
\newblock {\scriptsize\url{http://www.numberworld.org/y-cruncher/}}
\newblock \en{[Accessed 21/06/2020]}\de{[abgerufen 21.06.2020]}.



\end{thebibliography}
}
